\documentclass[11pt,a4paper,sans]{moderncv} % Font options: 'sans' or 'roman'

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}   % Color options: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', and 'black'

% Adjust the page margins
\usepackage[scale = .82]{geometry}
% \usepackage{hyperref}
% \href{https://www.youtube.com/@grantsmith3653/featured}{YouTube}
% 


% Personal data
\name{Developer Advocate}{Grant Smith}
\address{550 Stoneridge Dr Apt C206}{Lawrence Kansas, 66049}{}
\phone[mobile]{+1~(913)~660~5415}
\email{14.gsmith.14@gmail.com}
\social[linkedin]{grant-smith-895b64a4}
\social[github]{GSmithApps}
% \homepage{www.johndoe.com}
% \photo[64pt][0.4pt]{example-image} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A quote from you, if you wish"}

\begin{document}

\makecvtitle % Print the CV title


\section{Community Engagement and Content Creation}
\cventry{2022--2022}{Meetup Presenter}{\href{https://www.meetup.com/east-bay-tri-valley-machine-learning-meetup/}{East Bay Machine Learning Meetup}}{Virtual}{}{Has presented six times within the last year on various deep learning topics.}
\cventry{2022--2022}{Career Fair Representative}{\href{https://www.securitybenefit.com/splash-page}{Security Benefit}}{Various}{KS}{Go-to representative for career fairs.  Found and hired two interns, one of whom we hired full time, and the other of whom
was my report and we are hoping to hire full time at the end of the year.}
\cventry{2022--2022}{Content Creator (Personal)}{\href{https://www.youtube.com/@grantsmith3653/featured}{YouTube}, \href{https://medium.com/@14.gsmith.14}{Medium}, \href{https://github.com/GSmithApps}{Github}, \href{https://www.kaggle.com/grannysmithapples}{Kaggle}}{}{}{Has lightly been making Youtube videos and other content for the last 6 years.}

\section{Teaching Experience}
\cventry{2021--2022}{Data Analytics Boot Camp Instructor}{\href{https://www.edx.org/boot-camps/data-analytics?linked_from=sitenav}{EdX / Ohio State University}}{Virtual}{}{Taught an online data analytics boot camp.%
    \begin{itemize}%
    \item 5 star rating from each student -- in both review to EdX and Rate My Professor.
    \item Taught the class in the evenings while working full time.
    \end{itemize}
}
\cventry{2022}{Pre Calculus Instructor}{The University of Kansas}{Lawrence}{KS}{Taught two classes of pre-calculus at The University of Kansas.%
    \begin{itemize}%
    \item Also 5 star rating from each student -- in both review to KU and Rate My Professor.
    \end{itemize}
}

\section{Work Experience}

\cventry{2022--Present}{Quantitative Developer}{\href{https://www.securitybenefit.com/splash-page}{Security Benefit}}{Topeka}{KS}{Worked on our derivative valuation software.
    \begin{itemize}
    \item Initiated our documentation effort.
    \item Was part of our leadership group.
    \end{itemize}
}

\cventry{2020--2021}{Business Intelligence Developer}{Black and Veatch}{Overland Park}{KS}{Developed business intelligence solutions with Power BI and other BI and data engineering tools.\newline{}%
}
\cventry{2019--2020}{Software Developer, Implementation Engineer}{\href{https://www.prometheusgroup.com/solutions/asset-performance-management-software}{Atonix Digital (Black and Veatch Subsidiary, now owned by Prometheus Group)}}{Overland Park}{KS}{Began on the implementation team to onboard new clients. Worked way into role on the development team.\newline{}%
}
\cventry{2016--2019}{Data Manager, Chemical Engineer}{
    \href{https://www.bv.com/industries/gas-fuels-chemicals}{Black and Veatch}
    }{Overland Park}{KS}{Began career as chemical engineer, but fell in love with programming. Redirected career toward that goal.\newline{}%
}



\section{Education}
\cventry{2022}{Mathematics, M.A.}{The University of Kansas}{Lawrence}{KS}{Spent a semeter as a master's student. Left early for quant opportunity.}
\cventry{2020}{Mathematics, M.A.}{University of Missouri Kansas City}{Kansas City}{MO}{Took a course in the evenings while working full time.}
\cventry{2012--2016}{Chemical Engineering, B.S.}{The University of Kansas}{Lawrence}{KS}{
\begin{itemize}
    \item Dean's List for academic achievement. 3.85 GPA.
    \item Was the president of his fraternity, which included managing 100+ students, 70+ of which lived in the house.
\end{itemize}
}  % Arguments can be left empty


\section{Comments From Peers}
\cvitem{Security Benefit}{
    % make an unordered list
    \begin{itemize}
        \item \textit{What I really appreciate about Grant is how proactive he is. Simply put, he makes problems go away.}
        \item \textit{I have not met a more team-first person than Grant.}
        \item \textit{I keep finding Grant's documentation in here and it keeps saving my butt.}
\end{itemize}    
}
\cvitem{Students}{
    \begin{itemize}
        \item \textit{Super friendly, kind, nice and caring. You can tell he truly
        loves what he does! definitely recommend and take again.}
        \item \textit{He has an uncanny ability to sense when your ADHD brain begins
        to zone out and immediately refocuses the class.}
    \end{itemize}    
    }
    
    \end{document}
    
    % \section{Languages}
    % \cvitemwithcomment{Language 1}{Skill level}{Comment}
    % \cvitemwithcomment{Language 2}{Skill level}{Comment}
    
    % \section{Computer skills}
    % \cvdoubleitem{Category 1}{Comment}{Category 4}{Comment}
    % \cvdoubleitem{Category 2}{Comment}{Category 5}{Comment}
    
    % \section{Interests}
    % \cvitem{Hobby 1}{Description}
    % \cvitem{Hobby 2}{Description}