
\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


% moderncv themes
\moderncvstyle{casual}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}
%\setlength{\makecvtitlenamewidth}{10cm}

% personal data
\name{Grant Smith}{}
\address{Lawrence Kansas}{}{}
\phone[mobile]{+1~(913)~660~5415}
\email{14.gsmith.14@gmail.com}
\social[linkedin]{grant-smith-895b64a4}
\social[github]{GSmithApps}

\title{Resumé title}


\begin{document}


\newcommand{\hiringmanager}{Hiring Manager}
\newcommand{\position}{Senior Producer (Programming, Computer Science, & Technology)}
\newcommand{\company}{Brilliant}

\recipient{\hiringmanager{}}{Brilliant}
\date{\today}
\opening{Dear \hiringmanager{}}
\closing{Best,}
\makelettertitle

I am applying to be a producer at Brilliant because
I think it would be great way to use my experience,
passion, and skills to be a part of a team and make
an impact.

I want to be a part of
Brilliant.  I have had a membership since before 2018, have the
lifetime membership, and have solved 1,320 problems (which I
know isn't a record).  And as I look through the career page,
it makes me happy to see pictures that say things like
"content to make content".  I also really like that
the fellow team members are come from all walks of life,
because I feel like my relationship with computer science,
teaching, and making content is unique as well. 
I also certainly share the
beauty and fascination with STEM -- I light
up when anyone mentions programming and math.

Regarding the role and applicant type, I see that we're
looking for someone with a strong background in data
science and mathematics education -- I taught a data
analytics course, I have a YouTube playlist of talks
I've given at deep learning meetups, and I've taught
precalculus at The University of Kansas.  Lastly on this,
pedagogy and clear explanation is a big deal to me, and
I am excited that that is a stated requirement of this
position, and I can finally be a pedagogy fanatic.

Specifically regarding the listed responsibilities:
I see the mention of meeting the distinct needs of adults
looking to learn computer science and AI, and that
is precisely what I did in the data analytics boot camp
that I taught.  I also see a note about developing
a voice that empowers learners, and I like this as well
because I think it is important to emphasize that computer
science is totally doable.

Regarding the section on "you", the applicant: I'm
beaming at the requirement of an excitement
with programming languages, because
learning programming languages is my
guilty pleasure. I am currently working through some
AGDA while also learning rust and Crafting Interpreters.
And in reference to the openness to change and experiment
with new formats and platforms, you'll see exactly that
in my own teaching. In my YouTube channel, I'm always
tinkering with a new video style, and on my other channels,
I've tried everything from Medium to Observable to GeoGebra.

Aside from the job posting, I'd like to mention a few
other things. First, is that my values are people first,
and beauty second. I got this from Grant Sanderson's talk
about ego in math.  I take the talk to mean that with our
professions, the value is in helping people, not quite as
much as getting value from making the math beautiful.

In conclusion, it makes me happy to even write this cover letter.
It would mean a lot to me to get to use my teaching
and passion more.
Please reach out to me with any questions or further
discussions. I enjoy talking on the phone or video call,
so please don't hesitate.


\vspace{0.5cm}


\makeletterclosing

\end{document}


%% end of file `template.tex'.
