\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{grey}

\usepackage[scale = .82]{geometry}

% Personal data
\name{Developer Advocate}{Grant Smith}
\address{Lawrence, Kansas}{}{}
\phone[mobile]{+1~(913)~660~5415}
\email{14.gsmith.14@gmail.com}
\social[linkedin]{grant-smith-895b64a4}
\social[github]{GSmithApps}

\begin{document}

\makecvtitle

\section{Summary}

An innovative and passionate programmer/teacher with
experience as a software developer, teacher, and chemical engineer.
Presenter at many meetups and creator of much online content
including YouTube videos, GeoGebra applets, and more.
Aspiring to work in developer advocacy, community development,
technical sales, or training/teaching.

\section{Current}
\cventry{2022--Present}{Quantitative Developer}{\href{https://www.securitybenefit.com/splash-page}{Security Benefit}}{Topeka}{KS}{A core developer on the heart of our software: our valuation engine.
    \begin{itemize}
        \item Implements financial models in Python.
        \item Initiated our documentation effort.
        \item Is part of our group leadership.
        \item Has given many trainings on topics such as
        Git, deep learning, and static sites for documentation.
        \item Performs as mentor and onboarding guide for new hires.
    \end{itemize}
}
\cventry{2021--Present}{\href{https://www.edx.org/boot-camps/data-analytics?linked_from=sitenav}{Data Analytics Boot Camp Instructor}}{EdX / Ohio State University}{Virtual}{}{Teaches an online data analytics boot camp.%
    \begin{itemize}%
        \item Covers many topics including Python, JavaScript, SQL, Tableau, machine learning, and more.
        \item Has earned a 5 star rating from each student -- in both
              review to EdX and \href{https://www.ratemyprofessors.com/ShowRatings.jsp?tid=2720862}{Rate-My-Professor}.
        \item Teaches the class in the evenings while working full time.
        \item Exercises autonomy and course design expertise to
              streamline and tailor the curriculum.
    \end{itemize}%
}

\section{Work Experience}
\cventry{2020--2021}{
    Business Intelligence Developer}{
        \href{https://www.bv.com}{Black and Veatch}}{
            Overland Park}{KS}{
                Developed business intelligence solutions with Power BI
                and other data engineering tools.  Was the onboarding
                guide and mentor to all three new hires in our group.}
\cventry{2019--2020}{Software Developer, Implementation Engineer}{
    \href{https://www.prometheusgroup.com/solutions/asset-performance-management-software}{
        Atonix Digital (Black and Veatch Subsidiary, now owned by Prometheus Group)}}{
        Overland Park}{KS}{
        Began on the implementation team to onboard new clients.
        Worked way into role on the development team. Was the onboarding
        guide/mentor/trainer to both new hires in our group}
\cventry{2016--2019}{Data Manager, Chemical Engineer}{
    \href{https://www.bv.com/industries/gas-fuels-chemicals}{Black and Veatch}}{
        Overland Park}{KS}{
            Began career as chemical engineer, but fell in love with programming.
            Redirected career toward that goal.}



\section{Community Engagement and Content Creation}
\cventry{2022--2022}
    {Meetup Presenter}
    {\href{https://www.meetup.com/east-bay-tri-valley-machine-learning-meetup/}{East Bay Machine Learning Meetup}}
    {Virtual}{}
    {\href{https://www.youtube.com/playlist?list=PLytZkHFJwKUf-P1Q_AD-hvYKyH0VREKWw}
        {Has presented five times within the last year
        on various deep learning topics.
        The meetup has around 20 attendees each time, and
        the recordings have 600 views on YouTube.}}
\cventry{2022--2022}{Career Fair Representative}
    {\href{https://www.securitybenefit.com/splash-page}{Security Benefit}}{Lawrence/Manhattan}{KS}
    {Is the go-to representative for career fairs.
    Found and hired two interns, both of which we hired full-time
    at the end of the internships.}
\cventry{2022--2022}{Content Creator (Personal)}
    {\href{https://www.youtube.com/@grantsmith3653/featured}{YouTube},
    \href{https://medium.com/@14.gsmith.14}{Medium},
    \href{https://github.com/GSmithApps}{Github},
    \href{https://www.kaggle.com/grannysmithapples}{Kaggle},
    \href{https://www.geogebra.org/u/gsmithapples}{GeoGebra},
    }
    {}{}{\href{https://www.youtube.com/@grantsmith3653/featured}{
        Has lightly been making Youtube videos and
        other content for the last 6 years.
        Has made 40 YouTube videos (2,000 views) and 52 GeoGebra applets.}}
            
            
            
\section{Education}
\cventry{2022}{\href{https://www.credly.com/badges/3c754523-d992-47d9-b500-d7b5b18daf92/public_url}{AWS Certified Cloud Practitioner}}{AWS}{Virtual}{}{}
\cventry{2022}{\href{https://mathematics.ku.edu/graduate-program}{Mathematics, M.A.}}{The University of Kansas}{Lawrence}{KS}{Spent a successful semeter as a master's student (4.0 gpa). Left early for quant opportunity.}
\cventry{2022}{Pre Calculus Instructor}{The University of Kansas}{Lawrence}{KS}{Taught two sections of pre-calculus as a master's student.%
    \begin{itemize}%
        \item Earned a 5 star rating from each student --
        in both review to KU and \href{https://www.ratemyprofessors.com/ShowRatings.jsp?tid=2771200}{Rate-My-Professor}.
    \end{itemize}%
}
\cventry{2012--2016}{\href{https://cpe.ku.edu}{Chemical Engineering, B.S.}}{The University of Kansas}{Lawrence}{KS}{
    \begin{itemize}
        \item \href{https://business.ku.edu/undergraduate-programs/degree-programs/minor-business}{Business minor.}
        \item \href{https://jayhawkglobal.ku.edu/leadership-certificate}{Leadership certificate.}
        \item Was on The Dean's List for academic achievement. 3.85 GPA.
        \item Was the president of his fraternity, which included
        managing 100+ students, 70+ of which lived in the house.
    \end{itemize}
}


\section{Comments From Peers}
\cvitem{Security Benefit}{
    \begin{itemize}
        \item \textit{What I really appreciate about Grant is how proactive he is. Simply put, he makes problems go away.}
        \item \textit{I have not met a more team-first person than Grant.}
        \item \textit{I keep finding Grant's documentation in here and it keeps saving my butt.}
    \end{itemize}
}
\cvitem{Students}{
    \begin{itemize}
        \item \textit{\href{https://www.ratemyprofessors.com/rating/35222252?utm_source=share&utm_medium=web&utm_campaign=prof_rating}{Super friendly, kind, nice and caring. You can tell he truly loves what he does! Definitely recommend and take again.}}
        \item \textit{\href{https://www.ratemyprofessors.com/rating/35209449?utm_source=share&utm_medium=web&utm_campaign=prof_rating}{He has an uncanny ability to sense when your ADHD brain begins to zone out and immediately refocuses the class.}}
    \end{itemize}
}


\end{document}
